\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}

\usepackage[scale=0.915]{geometry}
\usepackage{enumitem}
%======================================
\newcommand{\role}[4]{
  \vspace{0cm}
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ #3 & #4
    \end{tabular*}
    \vspace{-0.3cm}
}
%=======================================

\name{Matt}{Bowring}

\begin{document}

\makecvtitle
\vspace{-1.5cm}
\begin{center}
    603-247-0061 $|$ 
    \href{mailto:bowrango@gmail.com}{bowrango@gmail.com} $|$ 
    \color{blue} \href{https://www.linkedin.com/in/matt-bowring-463610149/}{LinkedIn} $|$
    \color{blue} \href{https://github.com/bowrango}{Github}
\end{center}
\vspace{-1cm}

\section{Experience}

\role
      {Software Engineer}{06/2022 ‐ Present}
      {The MathWorks (Math/PDE Team)}{Natick, MA}

{\begin{itemize}[leftmargin=0.5cm, label={\textbullet}]

\item Sole developer and maintainer of the {{\color{blue}\href{https://www.mathworks.com/help/matlab/quantum-computing.html?s_tid=CRUX_lftnav}{MATLAB Support Package for Quantum Computing}}}; Contribute features for building quantum circuits, state-vector simulation, and OpenQASM generation to run on quantum hardware hosted by AWS and IBM. 4000+ downloads from academic and industry customers with more than 250k total executions on quantum hardware.

\item Contribute MATLAB scripts of quantum algorithms (VQE, QAOA, etc.) for external conferences, {{\color{blue}\href{https://github.com/mathworks/Quantum-Computing-MATLAB}{Github}}}, and documentation; Integrate third-party C++ libraries using CMake and MATLAB MEX; Meet weekly with industry partners to discuss on-going feature integration; Review and assist with documentation, quality engineering and marketing efforts; Participate in book clubs for quantum computing and numerical computing. 

\item Develop MATLAB scripts for industry customers researching quantum methods for constrained combinatorial optimization and classification. Meet regularly to discuss technical aspects and logistics for publishing external blogs and other material.

\end{itemize}}

\role
      {Application Engineer}{05/2021 ‐ 6/2022}
      {The MathWorks (Control, Design, and Automation Team)}{Natick, MA}

{\begin{itemize}[leftmargin=0.5cm, label={\textbullet}]

\item Supported 100s of customers with control engineering applications using MATLAB and Simulink. Collaborated with development teams to reproduce and resolve issues; Presented on customer applications to product teams, mentored interns and occasionally interviewed applicants.

\item Developed MATLAB scripts to build Hamiltonian for arbitrary course-grained protein folding on a lattice. Evaluated problems on D-Wave quantum annealer to compare binary fold encoding methods; Wrote MATLAB scripts to compute energy spectra of single qubit modelled in various coupling schemes of electromagnetic fields; Implemented methods to decompose controlled quantum gates with additional qubits in MATLAB.

\item Implemented and evaluated discrete-time dynamic graph network on QM7-X dataset to predict minimum energy molecule configurations using MATLAB. Collaborated with Deep Learning Toolbox developers with association from Cornell University to extend upon previous network that only classified equilibrium configurations.

\end{itemize}}

\section{Education}

\role
      {B.S. Mechanical Engineering}{2017 ‐ 2021}
      {The University of New Hampshire (3.8 GPA)}{Durham, NH}

{\begin{itemize}[leftmargin=0.5cm, label={\textbullet}]

\item Worked with student team to improve quadcopter path tracking using software-in-the-loop simulations of PX4 flight controller in Gazebo environment; Wrote MATLAB scripts modelling the controller to facilitate PID gain tuning; Deployed model on testbed quadcopter using ROS Python framework and analyzed flight data; Modelled isolated DC motor under disturbance using op-amp PID controller.

\item Lead student team in designing air intake for propulsion of mock jet engine using ANSYS and SolidWorks in collaboration with {{\color{blue}\href{https://www.jet-x.org/about.html}{Jet-X Engineering}}}; Ran CFD simulations of airflow to optimize driveshaft power of the turbine; Designed and 3D printed airfoils to be cast in aluminum using silicone mold created in vacuum chamber.

\item Worked on projects using OpenCV, Pytorch, and NetworkX Python libraries for camera calibration and graph clustering; Wrote MATLAB scripts to simulate temperature fields, material stresses, combustion engine cycles, rigid body motion, and RLC circuits for various academic projects. 

\item Tutored courses in thermodynamics, numerical computing, and mechanics; Mentored weekly at Makerspace to assist with 3D printers, laser cutter and other equipment; Volunteered weekly for STEM outreach with elementary students; Maintained routine weightlifting and attended hiking clubs.

\end{itemize}} 

\end{document}